Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-06-16 paper.qmd
Added section descriptions

The paper is organized as follows. @sec-background provides a summary of the literature on NLDR, and high-dimensional data visualization methods. @sec-method contains the details of the new methodology, including simulated data examples. Two applications illustrating the use of the new methodology for bioinformatics and image classification are in @sec-applications. Limitations and future directions are provided in @sec-discussion.

<!-- Where are sections 4 & 5 in this description? -->

@@

## Assessing the best fit, and hence most accurate \gD{} layout

@@

## Curiosities about NLDR results discovered by examining the model in the data space

>>>>

The paper is organized as follows. @sec-background provides a summary of the literature on NLDR, and high-dimensional data visualization methods. @sec-method contains the details of the new methodology, including simulated data examples. In @sec-bestfit, we describe how to assess the best fit and identify the most accurate \gD{} layout based on the proposed model diagnostics. Curiosities and unexpected patterns discovered in NLDR results by examining the model in the data space are discussed in @sec-curiosities. Two applications illustrating the use of the new methodology for bioinformatics and image classification are in @sec-applications. Limitations and future directions are provided in @sec-discussion.

@@

## Assessing the best fit, and hence most accurate \gD{} layout {#sec-bestfit}

@@

## Curiosities about NLDR results discovered by examining the model in the data space {#sec-curiosities}
